---
title: "hw0"
author: "Lola Wang"
format: html
editor: visual
execute:
  echo: false
---

## Question

1.  Write a Quarto document that defines variables $a=1, b=3, c=2$ and print out the solutions to $f(x)=ax^2+bx+c=0$. Do not report complex solutions, only real numbers.
2.  Include a graph of $f(x)$ versus $x$ for $x\in(-5,5)$.

## Answer

### 1. Solutions

```{r}

# change the coefficients here
a = 1
b = 3
c = 2
```

According to the equation $f(x)=ax^2+bx+c=0$, the solution of x should be $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$.

First, we can determine the number of solutions by looking $b^2-4ac$:

-   if positive, the equation will have **two** unique solutions

-   if equals zero, the equation will have exact **one** solution

-   if negative, the equation will have **no real (zero)** solution

```{r}

# calculate the number of solutions
det = b^2 - 4*a*c
sprintf('For our case a = %.0f, b = %.0f, c = %.0f, the result is %.1f.',a,b,c,det)

# print the results based on the number of solutions
if (det > 0){
  print('There will be 2 unique solutions.')
  x1 = (-b + sqrt(b**2 - 4*a*c))/(2*a)
  x2 = (-b - sqrt(b**2 - 4*a*c))/(2*a)
  sprintf('The solutions are x1 = %.1f, x2 = %.1f.',x1,x2)
  }else if (det == 0){
  print('There will be exact 1 solution.')
  x = (-b + sqrt(b**2 - 4*a*c))/(2*a)
  sprintf('The exact solution is x = %.1f.',x)
  }else{
  print('There will be 0 solution.')
}
```

### 2. Graph

We can double check our solution by plotting the graph and look for the intersects between the quadratic equation and y = 0.

```{r}
par(mfrow = c(1, 2))

# plot the equation: x in (-5,5)
x <- seq(-5, 5, length = 300)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h = 0, lty = 2)
title(main = "plot the equation: x in (-5,5)")

# based on the axis of symmetry
mid = -b/(2*a)
x <- seq(mid-2, mid+2, length = 300)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h = 0, lty = 2)
title(main = "based on the axis of symmetry")
```

```{r}

```
